Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-03-17 MCQMC2022ChallengesQMCSoftwareArticle.tex
Updates from Overleaf

%%%%%%% Author sign off on this first submission, last revision 3/17/2023
% Sou-Cheng Choi signed off on 3/17/20223
% Yuhan Ding signed off on
% Fred J. Hickernell signed off on 3/17/2023
% Jagadeeswaran Rathinavel signed off on
% Aleksei Sorokin signed off on 3/17/2023

@@

\subsection{LD Sequence Generators} A lattice, digital sequence, or Halton sequence generator typically supplies the sequence $\bsx_1, \bsx_2, \ldots$.  These sequences may be deterministic or random and are intended to have an empirical distribution that approximates well the uniform distribution.  Figure \ref{CDHJSfiglatticepts} illustrates an example of a lattice sequence.

@@

In fact, QMCPy is designed not simply to contain our own algorithms.  It is designed to serve as a middleware framework, allowing users to tap into a collection of QMC libraries originally written in various languages by different researchers at different times. Using object-oriented design, QMCPy specifies a few  extensible high-level mathematical objects as described in this section and in \cite{ChoEtal22a}. Developers of other (Q)MC software can  extend these objects to incorporate their existing algorithms by a combination of mechanisms: object inheritance, Python package inclusion, direct code translation, and/or interfaces to compiled C or Java libraries.

@@

	\item $g\lambda$ is the unnormalized Bayesian posterior density multiplied by parameter of interest \cite{GelEtal13}.
\end{itemize}

>>>>

%%%%%%% Author sign off on this first submission, last revision 3/17/2023
% Sou-Cheng Choi signed off on 3/17/20223
% Yuhan Ding signed off on
% Fred J. Hickernell signed off on 3/17/2023
% Jagadeeswaran Rathinavel signed off on 3/17/2023
% Aleksei Sorokin signed off on 3/17/2023

@@

\subsection{LD Sequence Generators} A lattice, digital sequence, or Halton sequence generator typically supplies the sequence $\bsx_1, \bsx_2, \ldots$.  These sequences may be deterministic or random and are intended to have an empirical distribution that approximates well the uniform distribution.  Figure \ref{CDHJSfiglatticepts} illustrates an example of a (randomly shifted) lattice sequence.

@@

In fact, QMCPy is designed not simply to contain our own algorithms.  It is designed to serve as a middleware framework, allowing users to tap into a collection of QMC libraries originally written in various languages by different researchers at different times. Using the object-oriented design, QMCPy specifies a few  extensible high-level mathematical objects as described in this section and in \cite{ChoEtal22a}. Developers of other (Q)MC software can  extend these objects to incorporate their existing algorithms by a combination of mechanisms: object inheritance, Python package inclusion, direct code translation, and/or interfaces to compiled C or Java libraries.

@@

	\item $g\lambda$ is the unnormalized Bayesian posterior density multiplied by the parameter of interest \cite{GelEtal13}.
\end{itemize}
